\documentclass[letterpaper,11pt]{article}
\usepackage{hyperref}
\usepackage{geometry,amsmath,amsfonts}
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}
\usepackage{etaremune,enumerate}

\def\name{Leonid Petrov}
\def\footerlink{https://lpetrov.cc}
\allowdisplaybreaks
\usepackage{longtable}

\hypersetup{
  colorlinks = true,
  urlcolor = blue,
  pdfauthor = {\name},
  pdftitle = {\name},
  pdfsubject = {Leonid Petrov},
  pdfpagemode = UseNone
}

\geometry{
  body={6.2in, 8.25in},
  left=1.2in,
  top=1.45in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
% \renewenvironment{itemize}{
%   \begin{list}{}{
%     \setlength{\leftmargin}{1.5em}
%   }
% }{
%   \end{list}
% }

\begin{document}

{\huge \name{}. Curriculum Vitae}
\medskip

\textbf{For a brief version see \url{https://lpetrov.cc/research/petrovCVbrief.pdf}}

\noindent\hrulefill

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}


\begin{minipage}{0.45\linewidth}
	Department of Mathematics\\ University of Virginia\\ 141 Cabell Drive,
	Kerchof Hall\\ P.O. Box 400137\\ Charlottesville, VA 22904-4137
\end{minipage}
\begin{minipage}{0.45\linewidth}
	\begin{tabular}{ll}
		Office Phone: & +1-434-924-4167                           \\
		Email:        &
		\href{mailto:petrov@virginia.edu}{\tt petrov@virginia.edu}\\&
		\href{mailto:lenia.petrov@gmail.com}{\tt
			lenia.petrov@gmail.com}
		\\
		Homepage:     & \url{https://lpetrov.cc} \\

		\\
		ORCID:     & \href{https://orcid.org/0000-0003-4607-7399}{\texttt{0000-0003-4607-7399}} \\
	\end{tabular}
\end{minipage}

\section*{Research areas}

Probability, Mathematical Physics, Algebraic Combinatorics, Representation
Theory.

\section*{Education}

\begin{itemize}
	\item
	      [2007--2010:]
	      Ph.D. studies,\\Institute for Information Transmission Problems
	      (Moscow, Russia). \\ Advisor:
	      \href{http://www.iitp.ru/en/userpages/88/}{Grigori Olshanski}.\\ Thesis
	      ``Markov Chains on Partitions and Infinite--Dimensional Diffusion Processes''.
	      %defended June 21, 2010

	\item
	      [2002--2007:]
	      Diploma with excellence,\\ Lomonosov Moscow State University
	      (Russia),\\ Department of Mathematics and Mechanics, specialization in Probability.

	\item
	      [1997--2002:] Moscow High School No. 2.
\end{itemize}

\section*{Appointments}

\begin{itemize}
	\item
	      [Since 2024:]
	      Professor\\ at Department of Mathematics, University
	      of Virginia, Charlottesville, VA, USA.
	\item
	      [2019--2024:]
	      Associate Professor\\ at Department of Mathematics, University
	      of Virginia, Charlottesville, VA, USA.
	\item
	      [2014--2019:]
	      Assistant Professor\\ at Department of Mathematics, University
	      of Virginia, Charlottesville, VA, USA.
	\item
	      [2011--2014:]
	      Research Instructor\\ at Department of Mathematics, Northeastern
	      University, Boston, MA, USA.
	\item
	      [2009--2011:]
	      Research associate\\ at Dobrushin Mathematics Laboratory,
	      Institute for Information Transmission Problems, Moscow, Russia.
\end{itemize}

\section*{Visiting Appointments}

\begin{itemize}
	\item [Spring 2024:]
		  Senior Fellow
		  \\
		  IPAM Program ``Geometry, Statistical Mechanics, and Integrability''
	\item [Fall 2021:]
		  Research Professor
		  \\
		  MSRI Program ``Universality and Integrability in Random Matrix Theory and Interacting Particle Systems''
	\item
	      [2017--2018:]
	      Visiting Assistant Professor\\ at Department of Mathematics, MIT,
	      Cambridge, MA, USA.
\end{itemize}

\section*{Recent prizes/funding}
\begin{itemize}
	\item [2025--2030:]
	Simons Foundation International Travel Support for Mathematicians SFI-MPS-TSM-00013561
	``Combinatorial Structures at Large Scale through Integrability'',
	\$42,000.

	\item [2022--2026:]
	NSF DMS grant 2153869
	``Random Systems from Symmetric Functions and Vertex Models'',
	\$320,654.

	\item [2022--2024:]
	4-VA at UVA Collaborative Research Grant program
	``Randomness by algebraic structures'',
	\$30,000.
	\item [2020--2025:]
		Simons Collaboration Grant for Mathematicians 709055
		``Distributional symmetries in stochastic systems'',
		\$42,000.
	\item [2019:]
		The 2020 Bernoulli prize for an outstanding survey article in probability
		(jointly with Alexei Borodin for the paper \emph{Integrable probability: From representation theory to
		Macdonald processes})
	\item
				[2018-2019:]
				PI, NSF DMS conference grant
				1839534
				``Workshop on Representation Theory, Combinatorics, and Geometry'',
				\$15,000
				(PI with co-PIs Jennifer Morse and Weiqiang Wang).
	\item
	      [2017:] Simons Foundation Collaboration Grant for
	      Mathematicians. Recommended for funding but not awarded due to
	      the receipt of the NSF DMS grant 1664617 (as per the rules of Collaboration
	      Grants).
	\item
	      [2017--2022:] PI, NSF DMS grant 1664617
	      ``FRG: Collaborative Research: Integrable Probability''.
	      Joint with PIs Jinho Baik (University of Michigan), Alexei
	      Borodin, Vadim Gorin (MIT), and Ivan Corwin (Columbia University). Amount:
	      \$193,453 (UVA part).
	\item
	      [2016--2017:]
	      Co-PI, NSF DMS conference grant 1663552 ``2017 Seminar on Stochastic
	      Processes'', \$46,020.00 (co-PI with PI Tai Melcher and another co-PI
	      Christian Gromoll).
	% \item
	%       [2015:] Prize of the Moscow Mathematical Society.
	% \item
	%       [2014--2015:] EDF Fellowship of the University of Virginia.
	% \item
	%       [2014:] AMS/NSF Travel Grant Award for ICM 2014.
%	\item
%	      [2011--2013:] RFBR--CNRS grant 11-01-93105 ``Representation
%	      theory and noncommutative geometry''.
%	\item
%	      [2010--2012:] RFBR--CNRS grant 10-01-93114 ``New models of
%	      Markov processes on point configurations. Applications to
%	      stochastic queueing networks''.
%	\item
%	      [2010:] Dynasty foundation fellowship for young scientists.
%	\item
%	      [2010:] Silver prize of The Fourteenth M\"obius Contest.
%	\item
%	      [2009:] Alexander Kuznetsov/Independent University of Moscow
%	      graduate student scholarship.
%	\item
%	      [2005, 2006:] V. Potanin federal scholarship for academic
%	      excellence, leadership and creativity.
\end{itemize}

\section*{Publications}

\subsection*{Preprints ($*$), accepted, or published}

\input{TEX_CV_publist.tex}

\section*{Students and postdocs}

\begin{enumerate}
    \item \href{https://math.virginia.edu/people/smb2tp/}{Yizhen Li}, UVA Ph.D. student 2024-29
    \item \href{https://mtikhonov.com}{Mikhail Tikhonov}, UVA Ph.D. student 2020-26
    \item \href{https://danielslonim.github.io}{Daniel Slonim}, UVA postdoc 2022-24 (now Tenure Track at Hillsdale College)
    \item \href{https://math.mit.edu/directory/profile.html?pid=2588}{Svetlana Gavrilova},  HSE bachelor thesis, 2020-21 (now Ph.D. student at MIT)
    \item \href{https://sites.google.com/view/axelsaenz}{Axel Saenz}, UVA postdoc 2016-19 (now Tenure Track at Oregon State)
\end{enumerate}

\section*{Organization and service}

\begin{itemize}
	\item [2026:]
	\href{https://www.coinflippers.org/}{Coin Flippers 2026: The ICM Satellite Edition},
	University of Delaware,
	Newark, DE,
	July 21-22, 2026.

	\item [2026:]
	\href{https://jointmathematicsmeetings.org/jmm}{AMS Special Session on Random Tilings, Random Permutations, and Particle Systems},
	Joint Mathematics Meetings,
	Washington, DC,
	January 4-7, 2026.

	\item [2025:]
	Section at the
	\href{https://www.math.miami.edu/mca/}{Mathematical Congress of the Americas 2025},
	University of Miami,
	Miami, FL,
	July 21-25, 2025.

	\item [2025:]
	\href{https://aimath.org/pastworkshops/roadtokpz.html}{AIM workshop
	``All roads to the KPZ universality class''},
	AIM, Caltech, Pasadena, CA, March 17-21, 2025.

	\item [2024:]
	\href{https://math.virginia.edu/2024/09/BlueRidgeProb/}{Blue Ridge Probability Day at University of Virginia},
	October 4, 2024.

	\item [2024:]
	\href{https://lpetrov.cc/vipss2024/}{Virginia Integrable Probability Summer School 2024},
	July 8-19, 2024.

	\item [2024:]
	\href{https://math.virginia.edu/random-lie-2024/}{Workshop ``Randomness and Lie-Theoretic Structures at University of Virginia''},
	March 4-5, 2024.

	\item [2024:]
\href{https://www.jointmathematicsmeetings.org/meetings/national/jmm2024/2300_program_ss43.html}{AMS-AWM Special Session on Solvable Lattice Models and their Applications Associated with the Noether Lecture at the Joint Mathematics Meetings 2024},
San Francisco, CA, January 3-6, 2024.

\item [2023:]
\href{https://sites.google.com/view/sepc2023ii/sepc-2023-ii}{SouthEastern Probability Conference - II at University of Virginia},
August 14-15, Charlottesville, VA, 2023.

\item [2014-current:]
\href{http://math.virginia.edu/seminars/probability/}{University of Virginia Probability Seminar}

\item [2020, 2022:]
(postponed then canceled due to COVID)
\href{http://www.ams.org/meetings/sectional/2273_program.html}{Special Session on Integrable Probability at the 2020 AMS Spring Southeastern Sectional Meeting at University of Virginia},
March 13-15, 2020; March 11-13, 2022.

\item [2021:]
\href{https://www.matrix-inst.org.au/events/integrability-and-combinatorics-at-finite-temperature/}{Program "Integrability and combinatorics at finite temperature" at MATRIX Institute, Australia (virtual)},
June 7-18, 2021.

\item [2020:]
\href{http://mtikhonov.com/smisp/}{Online conference on Statistical Mechanics, Integrable Systems and Probability},
April 27 - May 1, 2020.

\item [2020:]
(postponed due to COVID)
\href{https://www.matrix-inst.org.au/events/integrability-and-combinatorics-at-finite-temperature/}{Program "Integrability and combinatorics at finite temperature" at MATRIX Institute, Australia},
June 1-19, 2020.

\item [2019:]
\href{http://vipss.int-prob.org/}{Virginia Integrable Probability Summer School 2019},
May 17 - June 8, 2019.

\item[2018-19:]
\href{https://lpetrov.cc/reading-2019/}{Reading seminar on Integrable Probability}.

\item [2018:]
\href{http://math.virginia.edu/ims/workshop-fall-2018/}{Workshop on Representation Theory, Combinatorics, and Geometry at University of Virginia},
October 19-21, 2018.

\item [2018:]
\href{http://frg.int-prob.org/conference2018/}{Conference "Integrable Probability Boston 2018 (IntProb Boston)" at MIT},
May 14-18, 2018.

\item [2017+:]
\href{http://frg.int-prob.org/}{Developer of the website and forum for the FRG "Integrable Probability"}.

\item [2017+:]
\href{http://math.virginia.edu/}{Developer of the University of Virginia Math Department website}.

\item [2017:]
\href{http://faculty.virginia.edu/ssp17/}{Conference "Seminar on Stochastic Processes 2017" at University of Virginia},
March 8-11, 2017.

\item [2016-17:]
\href{https://lpetrov.cc/2016/12/reading-seminar/}{Reading seminar on Integrable Probability}.

\item [2014-17:]
\href{http://math.virginia.edu/seminars/mathclub/}{Undergraduate Math Club at the University of Virginia}.
\end{itemize}

\section*{Talks and conferences}

% 2020:
% 1. Joint Mathematics Meetings 2020, Denver, CO, January 2020. Special session talk.
% 2. Workshop on Asymptotic Algebraic Combinatorics at IPAM (UCLA), Los Angeles, CA, February 2020.
% 3. University of Connecticut, Storrs, CT, February 2020. Colloquium and probability seminar.
% 4. (online) Russian Integrable Probability Seminar, April 2020.
% 5. (online) Institute for Information Transmission Problems, Moscow, Russia, May 2020. Seminar talk.
% 6. (online) CMI-HIMR Integrable Probability Summer School, August 2020.
% 7. (online) Central and invariant measures and applications, August 2020.
% 8. (online) New Connections in Integrable Systems, September 2020.
% 9. (online) UVA Math Circle, October 2020.
% 10. (online) Columbia University Integrable Probability Seminar, October 2020.
% 11. (online) Kansas State University, Representation Theory and Mathematical Physics Seminar, December 2020.

% 2021:
% 12. (online) Ohio State University, Combinatorics and Probability Seminar, February 2021.
% 13. (online) Stanford University, Solvable Lattice Models Seminar, February 2021.
% 14. (online) Ohio State University, Stochastic Spatial Processes Conference, March 2021.
% 15. (online) 10th World Congress in Probability and Statistics, July 2021. Invited session and prize session talk.
% 16. (online) Particle Systems and Partial Differential Equations (PSPDE) IX, July 2021.
% 17. (online) Sergei Kerov memorial conference, August 2021.
% 18. (online) Stanford University, Solvable Lattice Models Seminar, September 2021.
% 19. University of California, Davis, October 2021. Probability seminar.
% 20. University of California, Los Angeles, October 2021. Combinatorics seminar.
% 21. University of California, Berkeley, November 2021. Talk at an MSRI Program on random matrices.
% 22. Oregon State University, November 2021. Colloquium.

% 2022:
% 23. (online) 16th International Symposium on Orthogonal Polynomials, Special Functions and Applications, June 2022. Mini-symposium talk.
% 24. (online) University of Delaware, Probability Seminar, September 2022.
% 25. University of Colorado, Boulder, Probability Seminar, October 2022.
% 26. Stanford University, Solvable Lattice Models Seminar, November 2022.

% 2023:
% 27. University of Chicago, Probability and Statistical Physics Seminar, January 2023.
% 28. Simons Symposium on Solvable Lattice Models and Interacting Particle Systems, June 2023, Krün, Germany.
% 29. University of Warwick, Statistical Mechanics Seminar, June 2023.
% 30. Mini-course at the 2023 Workshop in Analysis and Probability at Texas A&M University, Graduate concentration week (Summer school), July 2023, College Station, TX.
% 31. The 43rd Conference on Stochastic Processes and their Applications (SPA2023), July 2023, Lisbon, Portugal. Contributed session talk.
% 32. IUPUI, Colloquium, September 2023, Indianapolis, IN.
% 33. The Asymmetric Simple Exclusion Process Conference, Simons Center for Geometry and Physics, October 2023, Stony Brook, NY.
% 34. MIT, Integrable Probability Working Group, October 2023, Cambridge, MA.
% 35. Duke University, Probability Seminar, November 2023, Durham, NC.
% 36. University of North Carolina, Chapel Hill, Physically Inspired Math Seminar, November 2023.
% 37. Panel on Best practices for AI integration in research and teaching at Mid-Atlantic Algebra, Geometry, and Combinatorics (MAAGC) Workshop, Virginia Commonwealth University, December 2023, Richmond, VA.

% 2024:
% 38. Queen Mary University of London, Probability and Applications Seminar, January 2024.
% 39. MPI Leipzig Oberseminar Analysis-Probability, Germany, January 2024.
% 40. Columbia University Integrable Probability Working Group, New York, NY, February 2024.
% 41. CUNY Probability Seminar, New York, NY, February 2024.
% 42. IPAM (UCLA) Program ``Geometry, Statistical Mechanics, and Integrability'' Opening Day and Tutorials mini-course, March 2024, Los Angeles, CA.
% 43. University of Southern California, Combinatorics Seminar, March 2024, Los Angeles, CA.
% 44. IPAM (UCLA) Program ``Geometry, Statistical Mechanics, and Integrability'' Workshop ``Integrability and Algebraic Combinatorics'', April 2024, Los Angeles, CA.
% 45. IPAM (UCLA) Program ``Geometry, Statistical Mechanics, and Integrability'' Workshop ``Vertex Models: Algebraic and Probabilistic Aspects of Universality'', May 2024, Los Angeles, CA.
% 46. IPAM (UCLA) Program ``Geometry, Statistical Mechanics, and Integrability'' Culminating Workshop, June 2024, Lake Arrowhead, CA.
% 47. Conference ``Representation Theory and Probability'' dedicated to Grigori Olshanski, October 2024, Leipzig, Germany.



\subsection*{Seminar talks}

\begin{longtable}{llc}
		2026, March
		& Stanford University, Stanford, CA (Probability seminar)
		\\
		& University of California, Berkeley (Probability seminar)
		\\\\
		2025, October
		& The Ohio State University, Columbus, OH (Probability seminar)
		\\\\
		2025, June
		& Carnegie Mellon University\\ & Seminar on AI in Math Teaching (online)
		\\\\
		2025, March
		& Rutgers University, Piscataway, NJ
		\\
		& Symmetric Functions and Probability Seminar
    \\\\
    2025, February
    & University of Illinois at Urbana-Champaign,
    \\
    &
    Colloquium and Integrability and Representation Theory Seminar (2 talks)
    \\\\
    2024, March
    & University of Southern California,
    Combinatorics Seminar, Los Angeles, CA
    \\\\
	2024, February
	& CUNY Probability Seminar, New York, NY
	\\
	& Columbia Integrable Probability Working Group, New York, NY
	\\\\
	2024, January
	& MPI Leipzig Oberseminar Analysis-Probability, Germany,
	\\
	& QMUL Probability and Applications Seminar, UK
	\\\\
	2023, November
	& Duke Probability Seminar, Durham, NC
	\\
	& Physically Inspired Math at UNC, Chapel Hill, NC
	\\\\
	2023, October
	& MIT Integrable Probability Working Group, Cambridge, MA
	\\\\
	2023, September
	& Colloquium at IUPUI, Indianapolis, IN
	\\\\
	2023, June
	& Statistical Mechanics Seminar at University of Warwick
	\\\\
	2023, January
	& Probability and Statistical Physics Seminar at University of Chicago
	\\\\
	2022, November
	& Solvable Lattice Models Seminar, Stanford (online)
	\\\\
	2022, October
	& Probability Seminar at University of Colorado, Boulder
	\\\\
	2022, September
	& Probability Seminar at University of Delaware (online)
	\\\\
	2021, November
	& Oregon State University, Colloquium
	\\
	& Talk at MSRI Program on random matrices
	\\\\
	2021, October
	& University of California, Davis
	\\
	& University of California, Los Angeles
	\\\\
	2021, September
	& Solvable Lattice Models Seminar, Stanford (online)
	\\\\
	2021, February
	& Solvable Lattice Models Seminar, Stanford (online)
	\\
	&
	Combinatorics and Probability Seminar at The Ohio State University (online)
	\\\\
	2020, December
	& Representation Theory and Mathematical Physics Seminar at KSU (online)
	\\\\
	2020, October
	& Columbia University Integrable Probability Seminar (online)
	\\
	&
	UVa Math Circle (online)
	\\\\
	2020, May
	& Institute for Information Transmission Problems
	(Dobrushin Lab Seminar, online)
	\\\\
	2020, April
	& Russian Integrable Probability Seminar (online)
	\\\\
	2020, February
	& University of Connecticut (colloquium and probability seminar)
	\\\\
	2019, November
	& University of Virginia (Department of Physics)
	\\\\
	2019, September
	& Tulane University
	\\\\
	2019, May
	& Virginia Tech
	\\\\
	2019, February
	& Kansas State University \\
	& University of Kansas (colloquium)
	\\\\
	2019, January
	& University of Minnesota
	\\\\
	2018, December
	& Rutgers University
	\\\\
	2018, November
	& University of Utah
	\\\\
	2018, October
	& University of Warwick
	\\\\
	2018, May
	& MIT
	\\\\
	2018, March
	& MIT
	\\\\
	2018, February
	& University of California, Davis
	\\
	& University of California, San Diego
	\\
	& University of California, Los Angeles
	\\\\
	2018, January
	& Skoltech Center for Advances Studies (Moscow, Russia)
	\\\\
	2017, November
	& Columbia University
	\\
	& Northeastern University
	\\\\
	2017, October
	& Brandeis University
	\\\\
	2017, August
	& Institute for Information Transmission Problems
	(Dobrushin Lab Seminar)
	\\\\
	2017, January
	& Case Western Reserve University
	\\\\
	2016, May
	& MIT
	\\\\
	2016, March
	& University of Rochester
	\\\\
	2016, March
	& University of California, Davis
	\\\\
	2016, January
	& University of Wisconsin, Madison
	\\\\
	2015, December
	& MSU (Meeting of the Moscow Mathematical Society)
	\\\\
	2015, October
	& Penn/Temple Probability Seminar
	\\\\

	2015, August
	& Institute for Information Transmission Problems
	(Dobrushin Lab Seminar)
	\\\\

	2015, May
	& Imperial College London
	\\\\

	2015, March
	& University of Michigan
	\\\\

	2014, November
	& Virginia Tech\\\\

	2014, September
	& Duke University\\\\

	2014, February
	& MIT\\\\

	2014, January
	  & Purdue University & \hspace{110pt}
	\\& University of British Columbia \\\\

	2013, December
	& University of Colorado, Boulder
	\\&Penn State University\\&Worcester Polytechnic Institute
	\\&University of Virginia\\&
	Carnegie Mellon University \\\\

	2013, November&
	University of Minnesota \\&
	Penn State University \\\\

	2013, October&
	University of Southern California
	\\&
	University of California, Los Angeles
	\\&Rutgers University\\\\

	2013, June& Institute for Information Transmission Problems
	(Dobrushin Lab Seminar)\\\\

	2013, March& Independent University of Moscow (General Seminar
	``Globus'')\\\\

	2013, February & Arizona State University\\\\

	2012, October & Princeton University \\
	& Columbia University\\\\

	2012, September & MIT \\\\

	2012, August
	& Institute for Information Transmission Problems
	(Yakov Sinai's Seminar)
	\\\\

	2012, March & New York University\\\\

	2011, October & Brown University \\
	&University of Michigan
	\\
	\\
	2011, May& Alfr\'ed R\'enyi Institute of Mathematics
	\\
	& Budapest University of Technology and Economics
	\\\\

	2008, October &
	St. Petersburg Department of Steklov Mathematical
	Institute% (Representation Theory and Dynamical Systems)
	\\
\end{longtable}
\bigskip

% In addition to that, I have presented results of my research in a number of
% talks given at various research seminars in Moscow, Russia (at Moscow State
% University, Institute for Information Transmission Problems, Independent
% University of Moscow, etc.) in 2005--2011, at Northeastern University, Boston,
% MA, USA in 2011--2014, and at University of Virginia, Charlottesville, VA, USA
% since 2014.


\subsection*{Conference talks}

\begin{etaremune}

\item Simons Symposium on Solvable Lattice Models and Interacting Particle Systems, August 2025, Kr\"un, Germany.

\item Mathematical Congress of the Americas 2025,
	University of Miami,
	July 2025, Miami, FL.
	\emph{Special session talk.}

\item (IP)$^3$ InterPlay between Integrable Probability and Interacting Particle systems,
 July 2025, Angers, France.

\item CMSA (Harvard) Program on Classical, quantum, and probabilistic integrable systems, May 2025,
Cambridge, MA.

\item AMS Spring Eastern Sectional Meeting,
	April 2025,
	Hartford, CT.
	\emph{Invited special session talk.}

\item
Conference ``Representation Theory and Probability'' dedicated to Grigori Olshanski,
October 2024, Leipzig, Germany.

	\item
		Culminating workshop of the
		IPAM Program ``Geometry, Statistical Mechanics, and Integrability'',
		June 2024, Lake Arrowhead, CA.
	\item
		Workshop
		``Vertex Models: Algebraic and Probabilistic Aspects of Universality''
		at
		IPAM Program ``Geometry, Statistical Mechanics, and Integrability'',
		May 2024, Los Angeles, CA.
	\item
		Workshop ``Integrability and Algebraic Combinatorics''
		at
		IPAM Program ``Geometry, Statistical Mechanics, and Integrability'',
		April 2024, Los Angeles, CA.
	\item
	IPAM Program ``Geometry, Statistical Mechanics, and Integrability''
	Opening Day and Tutorials mini-course, March 2024, Los Angeles, CA.
	\item
	Panel on Best practices for AI integration in research and teaching
	at
	Mid-Atlantic Algebra, Geometry, and Combinatorics (MAAGC) Workshop,
	Virginia Commonwealth University,
	December 2023,
	Richmond, VA.

	\item
	The Asymmetric Simple Exclusion Process Conference, Simons Center for Geometry and Physics, October 2023, Stony Brook, NY.

	\item
	The 43rd Conference on Stochastic Processes and their Applications (SPA2023), July 2023, Lisbon, Portugal.
	\emph{Contributed session talk.}

	\item
	Mini-course at the
	2023 Workshop in Analysis and Probability at Texas A\&M University, Graduate concentration week (Summer school). July 2023, College Station, TX.

	\item
	Simons Symposium on Solvable Lattice Models and Interacting Particle Systems, June 2023, Kr\"un, Germany.
	\item
	16th International Symposium on Orthogonal Polynomials, Special Functions and Applications (\emph{mini-symposium talk}).
	June 2022. Online.
\item
	Sergei Kerov memorial conference
	``New perspectives in asymptotic representation theory'',
	August 2021. Online, organized by CRM Montreal.
\item
	Particle Systems and Partial Differential Equations (PSPDE) IX,
	July 2021. Online and Braga, Portugal.
\item
	10th World Congress in Probability and Statistics (online),
	July 2021.
	Invited session and prize session talk.
\item
	Stochastic Spatial Processes at OSU (online),
	March 2021.
	Organized by Elliot Paquette and David Sivakoff.
\item New Connections in Integrable Systems (online),
	September 2020.
	Organized by Valentin Buciumas and Ole Warnaar.
\item
	Central and invariant measures and applications (online),
	August 2020.
	Organized by St. Petersburg Department of V. A. Steklov Mathematical Institute; Euler International Institute.
\item
	CMI-HIMR Integrable Probability Summer School (online),
	August 2020.
	Organized by
	Clay Mathematics Institute, the Heilbronn Institute for Mathematical Research,
	the Mathematical Institute at University of Oxford,
	and the NSF Integrable Probability Focused Research Grant.
\item
	Workshop on Asymptotic Algebraic Combinatorics at
	IPAM (UCLA), February 2020,
	Los Angeles, CA.
\item Joint Mathematics Meetings 2020,
	January 2020,
	Denver, CO.
	\emph{Invited special session talk.}
	\item
		BIRS Workshop ``Dimers, Ising Model, and their Interactions'',
		November 2019, Banff, Canada.
	\item AMS Fall Eastern Sectional Meeting
	at
	Binghamton University,
	October 2019,
	Binghamton, NY.
	\emph{Two special session talks.}
	\item
		Workshop New Trends in Integrable Systems,
		September 2019, Osaka, Japan.
	\item
		Workshop on Classical and Quantum Integrable
		Systems (CQIS-2019), July 2019, St. Petersburg, Russia.
	\item
		Summer School ``Contemporary Mathematics'' (mini-course in Russian for
		high school and beginning undergraduate students),
		July 2019, Dubna, Russia.
	\item
		BIRS Workshop ``Asymptotic Algebraic Combinatorics'',
		March 2019, Banff, Canada.
	\item Conference ``New Frontiers in Representation Theory'' dedicated to the 70th birthday of G.I.Olshanski, SkolTech Center for Advances Studies, January 2019, Moscow, Russia.
\item AMS Fall Eastern Sectional Meeting
	at University of Delaware,
	September 2018, Newark, DE.
		\emph{Special session talk.}
	\item
    The 40th Conference on Stochastic Processes and their
    Applications (SPA2018), June 2018,
		Gothenburg, Sweden.
		\emph{Invited session talk.}
	\item
		Integrable Probability Boston 2018 (IntProb Boston)
		Conference,
		MIT,
		May 2018,
		Cambridge, MA, USA.
	\item
		2018 Southeastern Probability Conference,
		Duke University,
		May 2018,
		Durham, NC, USA.
	\item
		``Non-equilibrium systems and special functions'' program at MATRIX Institute,
		January 2018,
		Creswick, Victoria, Australia.
	\item
		Meeting of the
		FRG ``Integrable Probability'', Columbia University,
		October 2017, New York, NY, USA.

	\item Chern-Simons Workshop
		``Integrability across mathematics and physics''
		 at University of California, Berkeley,
			September 2017, Berkeley, CA, USA.
	\item
	      International Workshop on Classical and Quantum Integrable
	      Systems (CQIS-2017), July 2017, Moscow, Russia.
	\item
	      The 39th Conference on Stochastic Processes and their
	      Applications (SPA2017), July 2017, Moscow, Russia.
				\emph{Invited session talk.}

	\item
	      PCMI Summer Session 2017 ``Random Matrices'', June--July 2017,
	      Park City, UT, USA.

	\item
	      Conference ``Qualitative Methods in KPZ Universality'', CIRM,
	      April 2017, Marseille, France.

	\item
	      Workshop on Asymptotic Representation Theory, Henri Poincar\'e
	      Institute, February 2017, Paris, France.

	\item
	      Clifford Lectures "Random Matrices, Combinatorics and Tiling
	      Problems" (main speaker: Pierre van Moerbeke) at Tulane University, November
	      2016, New Orleans, LA, USA.

	\item
	      Central Spring AMS Sectional Meeting at North Dakota State
	      University, April 2016, Fargo, ND, USA. \emph{Special session talk}.

	\item
	      Workshop ``Six-vertex model, dimers, shapes, and all that'' at
	      the Simons Center for Geometry and Physics, March 2016, Stony Brook, NY, USA.

	\item
	      Program ``New Approaches to Non-equilibrium and Random Systems:
	      KPZ Integrability, Universality, Applications and Experiments'' at the Kavli
	      Institute for Theoretical Physics, March 2016, Santa Barbara, CA, USA.

	\item
	      Workshop on Classical and Quantum Integrable Systems
	      (CQIS-2015), Institute for High Energy Physics, July 2015, Protvino, Russia.
	      Tutorial lecture \emph{``Integrable probability and Bethe   ansatz''}.

	\item
	      ``Random Interfaces and Integrable Probability'' workshop (part
	      of ``Statistical Mechanics, Integrability and Combinatorics''
	      program), Galileo Galilei Institute for Theoretical Physics, June 2015,
	      Florence, Italy.

	\item
	      ``Random Polymers and Algebraic Combinatorics'' workshop,
	      Mathematical Institute of the University of Oxford, May 2015,
	      Oxford, UK.

	\item
	      ``Limit shapes'' workshop, ICERM, April 2015, Providence, RI,
	      USA.   % \url{http://icerm.brown.edu/video_archive/videos/sp_s15_w3/Solving_interacting_particle_systems_by_Fourier-like_transforms_]_Leonid_Petrov,_University_of_Virginia.php}% online at% Video of the talk available

	\item
	      Central Spring AMS Sectional Meeting at Michigan State
	      University, March 2015, East Lansing, MI, USA. \emph{Special session talk}.

	\item
	      Columbia--Princeton Probability Day, March 2015, Princeton, NJ,
	      USA. I was one of the two junior speakers at a one-day seminar series, with a
	      talk \emph{``Eigenfunctions of stochastic integrable particle systems''}.

	\item
	      Inhomogeneous Random Systems conference, Henri Poincar\'e
	      Institute, January 2015, Paris, France.

	\item
	      International Congress of Mathematicians, August 2014, Seoul,
	      South Korea. \emph{Contributed talk}.

	\item
	      Workshop ``From Macdonald Processes to Hecke Algebras and
	      Quantum Integrable Systems'' at Henri Poincar\'e Institute, May 2014, Paris,
	      France.

	\item
	      Workshop ``Random Matrices and Jacobi Operators'' at
	      Mittag-Leffler Institute, May 2014, Stockholm, Sweden.

	\item
	      Columbia / Courant Joint Probability Seminar Series on
	      Kardar-Parisi-Zhang Universality. I was one of the three speakers of the
	      seminar series, with a talk \emph{``Markov Dynamics on Macdonald Processes''}.
	      October 2013, New York, NY, USA.

	\item
	      Cornell Probability Summer School, July 2013, Ithaca, NY, USA.
	      \emph{Tutorial sessions for the lecture course of A.~Borodin, and a short
		      talk}.

	\item
	      Random Tilings Workshop at the Simons Center for Geometry and
	      Physics, February 2013, Stony Brook, NY, USA.

	\item
	      MSRI ``Random Spatial Processes'' program, April 2012, Berkeley,
	      CA, USA.

	\item
	      Interacting Particle Systems, Growth Models, and Random Matrices
	      Workshop at the University of Warwick, March 2012, Warwick, UK.

	\item
	      International conference ``50 years of IITP'', July 2011,
	      Moscow, Russia.

	\item
	      EURANDOM Workshop YEP VIII 2011 ``Stochastic Models for
	      Population Dynamics'', March 2011, Eindhoven, Netherlands.

	\item
	      Mathematics -- XXI century. PDMI 70th anniversary, September
	      2010, St.~Petersburg, Russia.

	\item
	      PIMS/UBC School in Probability, June 2009, UBC, Vancouver,
	      Canada.

	\item
	      Summer School ``Large N Limits'', August 2008, Bitche, France.
\end{etaremune}

\subsection*{Research programs and focused collaborations}

\begin{etaremune}
\item
Simons Math Summer Workshop ``Algebraic methods in probability'',
July 5-18, 2026 (2 weeks).
\item AIM SQuaRE ``Combinatorics and Integrability of Interacting Particle Systems'', American Institute of Mathematics (August 2024, October 2025).
\item AIM SQuaRE ``Young tableau asymptotics'', American Institute of Mathematics (October 2019, January 2021 (virtual), February 2023, April 2024).
	\item
	IPAM Program ``Geometry, Statistical Mechanics, and Integrability'',
	Los Angeles, CA,
	March-June 2024.
	\item
	MSRI Program ``Universality and Integrability in Random Matrix Theory and Interacting Particle Systems'', Berkeley, CA, August 16 - December 17, 2021.
	\item
		``Non-equilibrium systems and special functions'' program at MATRIX Institute,
		January 2018,
		Creswick, Victoria, Australia (2 weeks).
	\item
	      PCMI Summer Session 2017 ``Random Matrices'', June--July 2017,
	      Park City, UT, USA (3 weeks).
	\item
	      Program ``New Approaches to Non-equilibrium and Random Systems:
	      KPZ Integrability, Universality, Applications and Experiments'' at the Kavli
	      Institute for Theoretical Physics (University of California, Santa Barbara),
	      February--March 2016, Santa Barbara, CA, USA (3 weeks).
	\item
	      Program ``Statistical Mechanics, Integrability and
	      Combinatorics'', Galileo Galilei Institute for Theoretical Physics, June 2015,
	      Florence, Italy (1 month).
\end{etaremune}

% \subsection*{Visits / membership in programs}

% \begin{etaremune}
% \item AIM SQuaRE ``Combinatorics and Integrability of Interacting Particle Systems'', American Institute of Mathematics,
% 	Los Angeles, CA,
% 	October 2025.
% 	\item AIM SQuaRE ``Combinatorics and Integrability of Interacting Particle Systems'', American Institute of Mathematics,
% 	Los Angeles, CA,
% 	August 2024.
% 	\item
% 	IPAM Program ``Geometry, Statistical Mechanics, and Integrability'',
% 	Los Angeles, CA,
% 	March-June 2024.
% 	\item AIM SQuaRE ``Young tableau asymptotics'', American Institute of Mathematics,
% 	Los Angeles, CA,
% 	April 2024.
% 	\item
% 	      Collaboration with Natasha Blitvic and Sasha Gnedin, Queen Mary University of London, January 2024, London, UK (3 weeks).
% 	\item AIM SQuaRE ``Young tableau asymptotics'', American Institute of Mathematics,
% 	San Jose, CA,
% 	February 2023.
% 	\item
% 	MSRI Program ``Universality and Integrability in Random Matrix Theory and Interacting Particle Systems'', Berkeley, CA, August 16 - December 17, 2021.
% 	\item
% 	AIM SQuaRE ``Young tableau asymptotics'', American Institute of Mathematics,
% 	January 2021 (virtual).
% 	\item
% 	AIM SQuaRE ``Young tableau asymptotics'', American Institute of Mathematics,
% 	San Jose, CA,
% 	October 2019.
% 	\item
% 		``Non-equilibrium systems and special functions'' program at MATRIX Institute,
% 		January 2018,
% 		Creswick, Victoria, Australia (2 weeks).
% 	\item
% 	      PCMI Summer Session 2017 ``Random Matrices'', June--July 2017,
% 	      Park City, UT, USA (3 weeks).
% 	\item
% 	      Collaboration with Daniel Orr, Virginia Tech, June 2016,
% 	      Blacksburg, VA, USA (4 days).
% 	\item
% 	      Program ``New Approaches to Non-equilibrium and Random Systems:
% 	      KPZ Integrability, Universality, Applications and Experiments'' at the Kavli
% 	      Institute for Theoretical Physics (University of California, Santa Barbara),
% 	      February--March 2016, Santa Barbara, CA, USA (3 weeks).
% 	\item
% 	      Program ``Statistical Mechanics, Integrability and
% 	      Combinatorics'', Galileo Galilei Institute for Theoretical Physics, June 2015,
% 	      Florence, Italy (1 month).
% 	\item
% 	      Collaboration with Ivan Corwin and Konstantin Matveev, Columbia
% 	      University, March 2015, New York, NY, USA (3 days).
% 	\item
% 	      Visit to Alfr\'ed R\'enyi Institute of Mathematics, May 2011,
% 	      Budapest, Hungary (1 week).
% \end{etaremune}

% \subsection*{Other events participated}

% \begin{etaremune}
% 	\item
% 	Workshop on Mathematical Physics in honor of Craig Tracy, UC Davis, October 2021, Davis, CA, USA.
% 	\item
% 	Bernoulli-IMS One World Symposium 2020 (online),
% 	August 2020.
% 	\emph{Integrable probability live discussion session moderator}.
% 	% \item
% 	% Program "Integrability and combinatorics at finite temperature"
% 	% at MATRIX Institute,
% 	% University of Melbourne,
% 	% June 2020,
% 	% Creswick, Victoria, Australia.
% 	% \item
% 	% FRG Conference on Integrable Probability IntProb New York, March 2020, Columbia University,
% 	% New York, NY.
% 	\item
% 	Meeting of the FRG ``Integrable Probability'', MIT, November 2018,
% 	Boston, MA, USA.
% 	\item
% 		Workshop ``Transport and localization in random media: theory and applications'',
% 		Department of Applied Physics and Applied Mathematics and Department of Mathematics,
% 		Columbia University,
% 		May 2018,
% 		New York, NY, USA.
% 	\item
% 		Eastern Spring AMS Sectional Meeting at Northeastern University,
% 	      April 2018, Boston, MA, USA.
% 	\item
% 		``Optimal and Random Point Configurations'' workshop, ICERM, February--March 2018, Providence, RI,
% 	      USA.
% 	\item
% 		Current Developments in Mathematics 2017, Harvard University, November 2017, Cambridge, MA, USA.
% 	\item
% 	      2017 Charles River Lectures on Probability Theory and Related
% 	      Topics, October 2017, Harvard University, Cambridge, MA, USA.
% 	\item
% 	      SouthEastern Probability Conference ``Interacting particle
% 	      systems'' (in honor of Professor Rick Durrett's 65th birthday), May 2017, Duke
% 	      University, Durham, NC, USA.

% 	\item
% 	      2016 Charles River Lectures on Probability Theory and Related
% 	      Topics, September 2016, MIT, Cambridge, MA, USA.

% 	      % \item Course Design Institute at the University of Virginia (a week-long training on designing courses focusing on student learning), June 2016, Charlottesville, VA, USA.

% 	\item
% 	      37th Midwest Probability Colloquium, Northwestern University,
% 	      October 2015, Evanston, IL, USA.

% 	\item
% 	      Workshop ``Analytic Tools in Probability and Applications'',
% 	      IMA, April 2015, Minneapolis, MN, USA.

% 	\item
% 	      Seminar on Stochastic Processes 2015 (\emph{with participation
% 		      in a panel discussion}), April 2015, University of Delaware, Newark, DE, USA.

% 	\item
% 	      Workshop on Moduli Spaces, Derived Geometry, and Geometric
% 	      Representation Theory, November 2014, University of North Carolina at Chapel
% 	      Hill, NC, USA.

% 	\item
% 	      2014 Charles River Lectures on Probability Theory and Related
% 	      Topics, October 2014, Harvard University, Cambridge, MA, USA.

% 	\item
% 	      Workshop ``Stochastic Analysis: Around the KPZ Universality
% 	      Class'' at Mathematisches Forschungsinstitut Oberwolfach, June 2014,
% 	      Oberwolfach, Germany.

% 	\item
% 	      2013 Charles River Lectures on Probability Theory and Related
% 	      Topics, October 2013, MIT, Cambridge, MA, USA.

% 	\item
% 		Gelfand Centennial Conference:
% 		A View of 21st Century Mathematics,
% 		August 2013, MIT, Cambridge, MA, USA.

% 	\item
% 	      Summer School ``KPZ equation and rough paths'', June 2013,
% 	      Lebesgue Center of Mathematics, Rennes, France.

% 	\item
% 	      2012 Charles River Lectures on Probability Theory and Related
% 	      Topics, October 2012, Microsoft Research, Cambridge, MA, USA.

% 	\item
% 	      St. Petersburg School in Probability and Statistical Physics,
% 	      June 2012, St. Petersburg, Russia.

% 	\item
% 	      Algebraic Geometry Northeastern Series (AGNES) Workshop, October
% 	      2011, Stony Brook, NY, USA.

% 	\item
% 	      Clay Institute Summer School ``Probability and Statistical
% 	      Physics in Two and more Dimensions'', July 2010, Buzios, Brazil.

% 	\item
% 	      Midrasha Mathematicae: The Mathematics of Oded Schramm, December
% 	      2010, Hebrew University, Jerusalem, Israel.

% 	\item
% 	      Summer School ``Structures in Lie Representation Theory'',
% 	      August 2009, Jacobs University, Bremen, Germany.

% 	\item
% 	      PROMYS summer program at Boston University for high school
% 	      students, Boston, MA, USA, 2001.
% \end{etaremune}

\section*{Teaching}


\begin{itemize}
\item[Fall 2025:]
    EGMT 1520 --- Building Truth from Scratch (first-year seminar).
\item[Spring 2025:]
    MATH 8380 --- Random matrices (graduate).
    \href{https://lpetrov.cc/rmt25/}{Course webpage with lecture notes}.

\item[Fall 2024:]
    MATH 2310 --- Calculus III, 2 sections.

\item[Fall 2023:]
	MATH 3100 --- Introduction to Probability, 2 sections.

\item[Spring 2023:]
	MATH 3340 --- Complex Variables with Applications.

\item[Fall 2022:]
	MATH 3100 --- Introduction to Probability.
	MATH 8852 --- Asymptotic Representation Theory (graduate topics course). \href{https://lpetrov.cc/art2022/}{Course webpage with lecture notes}.

\item[Spring 2022:]
	MATH 3100 --- Introduction to Probability, 3 sections.

\item[Spring 2021:]
	MATH 7370 Probability Theory II. Particle systems (graduate topics course). Online. \href{https://github.com/lenis2000/HTML_ParticleSysS21}{Lecture notes in Obsidian format}.
	Integrable particle systems (graduate topics course). Online; in Russian; at Independent University of Moscow.

\item[Fall 2020:]
	MATH 3100 --- Introduction to Probability, 2 sections. Online.

\item[Spring 2020:]
	MATH 3340 --- Complex variables. Partially online.
	MATH 7310 --- Real Analysis and Linear Spaces (graduate). Partially online.

\item[Fall 2019:]
	MATH 8380 --- Random matrices (graduate). \href{https://lpetrov.cc/rmt19/}{Course webpage with lecture notes}.

\item[Spring 2019:]
	MATH 7310 --- Real Analysis and Linear Spaces (graduate).

\item[Fall 2018:]
	MATH 3100 --- Introduction to Probability, 2 sections.

\item[Spring 2017:]
	MATH 3100 --- Introduction to Probability.

\item[Fall 2016:]
	MATH 2310 --- Calculus III, 2 sections.

\item[Summer 2016:] Participation in the \textbf{Course Design Institute} at the University of Virginia (a week-long training on designing courses focusing on student learning), June 2016, Charlottesville, VA, USA.

\item[Spring 2016:]
	MATH 8380 --- Random matrices. \href{https://github.com/lenis2000/RMT_Spring_2016}{Course webpage on github}.

\item[Fall 2015:]
	MATH 3100 --- Introduction to Probability.

\item[Spring 2015:]
	MATH 5110 --- Introduction to Stochastic Processes.

	\item
	      [Fall 2014:]
	      From 2014, at University of Virginia. \\ MATH 3100 --- Introduction to
	      Probability.

	\item
	      [Spring 2014:]
	      Northeastern University. \\ MATH 7241 --- Probability 1
	      (graduate).

	\item
	      [Fall 2013:]
	      Northeastern University. \\ MATH 3081 --- Probability and
	      Statistics, 2 sections.
	\item
	      [Spring 2013:]
	      Northeastern University. \\ MATH 4581 --- Statistics and
	      Stochastic Processes.
	\item
	      [Fall 2012:]
	      Northeastern University. \\ MATH 1342 --- Calculus II for
	      Sci\&Eng (honors section). Part of a teaching experiment at Department of
	      Mathematics with ``inverted'' sections: the instructor assigns watching
	      video-lectures accompanying the textbook for homework, and spends class-time
	      going over problems and clarifying the material.

	      MATH 7382 --- Topics in Probability (graduate): an expository
	      introductory-level graduate course on solvable probabilistic models, including
	      tools of algebraic combinatorics and representation theory.
		  \href{https://www.ams.org/open-math-notes/omn-view-listing?listingId=110813}{Lecture notes at AMS Open Notes}.

	\item
	      [Spring 2012:]
	      Northeastern University. \\ MATH 3081 --- Probability and
	      Statistics, 2 sections.
	\item
	      [Fall 2011:]
	      Northeastern University.\\ MATH 1342 --- Calculus II for
	      Sci\&Eng.
	\item
	      [Spring 2011:]
	      ``Math in Moscow'' programme in English for international
	      students at the Independent University of Moscow. A course in
	      Combinatorics.

	\item
	      [2007---2008:]
	      Moscow High School No. 17. Teacher of mathematics.
\end{itemize}

\section*{Editing and reviewing}

\begin{itemize}
	\item
	Member of the editorial boards at ``\href{https://www.springer.com/journal/11040}{\textbf{Mathematical Physics, Analysis and Geometry}}'', ``\href{https://escholarship.org/uc/combinatorial_theory/}{\textbf{Combinatorial Theory}}'', and ``\href{https://imstat.org/journals-and-publications/electronic-journal-of-probability/}{\textbf{Electronic Journal/Communications of Probability}}''.
	\item Program committee member for FPSAC (Formal Power Series and Algebraic Combinatorics),
		2017, 2021, and 2024.
	\item
	I regularly referee scholarly journal papers submitted to numerous journals,
	including
	Ann. Prob., Adv. Math., Adv. Appl. Math., Comm. Math. Phys., Intern. J. Math.,
	Arkiv f\"or Mat., SIGMA, J. Alg. Comb., Comm. Pure Appl. Math., Intern. Math.
	Res. Notices, J. Appl. Probab., J. Comb. Theory A, Symp. Th. Aspects of Comp.
	Sci., J. of Stat. Physics, Electron. Comm. Probab.
	\item
	I am a regular
	reviewer for the Mathematical Reviews database.
	\item
	I reviewed grant proposals and served on panels for several funding agencies.
\end{itemize}

% \section*{Other}
%
% \begin{itemize}
%   \item
%   I am broadening access to AI tools for working mathematicians by \href{https://lpetrov.cc/AI-math/}{sharing} \href{https://storage.lpetrov.cc/research_files/talks/AI_UVA_Oct10.pdf}{best practices} and participating in panel discussions. I also serve as an AI guide for Department of Mathematics, University of Virginia.
%
%
%   % \item
%   % Notes ``Lozenge tilings and random dynamics'' from the
%   % Summer School ``Contemporary Mathematics'' (in Russian, for
%   % high school and beginning undergraduate students),
%   % available at
%   % \url{https://lpetrov.cc/dubna2019/}
%
%   \item
%   Random tilings at an art exhibition
%
%   \url{https://www.radcliffe.harvard.edu/event/2016-art-discovery-exhibition}
%   \item
%   Course notes
%   ``Asymptotic representation theory'',
%   taught by G. Olshanski
%   at the Independent University of Moscow,
%   Fall 2009 and Spring 2010 (in Russian).
%   Available at \url{https://lpetrov.cc/art/}
%
% \end{itemize}



% Prepared lecture notes for the courses:
% \begin{enumerate}
%   \item A number of
%   undergraduate mathematical courses
%   at the Moscow State University,
%   including advanced probability courses
%   by A. Bulinski (2003--2006).

%   \item ``Statistical Mechanics and the Renormalisation Group''taught by D. Brydges
%   at the PIMS-UBC Summer School 2009.
%   Available at \\
%   \url{http://www.math.ubc.ca/~db5d/SummerSchool09/lectures-db/smrg.pdf}.

%   \item ``Asymptotic representation theory'',
%   taught by G. Olshanski
%   at the Independent University of Moscow,
%   Fall 2009 and Spring 2010 (in Russian).
%   Available at
%   \url{http://ium.mccme.ru/postscript/f09/representation.zip},
%   \url{http://ium.mccme.ru/postscript/s10/representation2.pdf}.

%   \item ``Topics in probability''
%   course I taught
%   at the Northeastern University,
%   Fall 2012. Available at
%   my homepage:
%   \url{http://faculty.virginia.edu/petrov/7382F12/LectureNotes.pdf}.

%   \item ``Integrable probability: From representation theory to Macdonald processes''
%   taught by A. Borodin (with tutorial sessions
%   given by myself)
%   at the Cornell Probability Summer School 2013.
%   See publication [15].
% \end{enumerate}

% Referee works submitted to various contests of the Independent University of Moscow (in particular, Moebius Contest, \url{http://www.moebiuscontest.ru/index-en.html}). Act as opponent on diploma thesis defences at the IUM.

% \smallskip

% For several years maintained web databases of mathematical seminar announcements at the Institute for Information Transmission Problems (Moscow, Russia).

% \smallskip

% My profile on MathOverflow: \url{http://www.mathoverflow.net/users/979/leonid-petrov}

% \medskip
%
% Informatic skills : \LaTeX, \texttt{Mathematica}, Computer experimentation,
% Probabilistic visualization, \texttt{git}, \texttt{Python},
% \texttt{html/jekyll} and web design, \texttt{UNIX}.
%
% \section*{Personal}
%
% \textbf{Date of birth:} November 5, 1985
%
% \textbf{Languages:} English (fluent), Russian (native)
%
% \textbf{Citizenship:} USA
%
% \textbf{Family:} Married, 2 children
%
% \textbf{Phone:} +1-857-210-7948

\bigskip

% Footer
\begin{center}
	\begin{footnotesize}
		Last updated: \today \\ \href{\footerlink}{\url{\footerlink}}
	\end{footnotesize}
\end{center}

\end{document}
