\documentclass[letterpaper,11pt]{article}
\usepackage{hyperref}
\usepackage{geometry,amsmath,amsfonts}
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}
\usepackage{etaremune,enumerate}

\def\name{Leonid Petrov}
\def\footerlink{https://lpetrov.cc}
\allowdisplaybreaks
\usepackage{longtable}

\hypersetup{
  colorlinks = true,
  urlcolor = blue,
  pdfauthor = {\name},
  pdftitle = {\name},
  pdfsubject = {Leonid Petrov},
  pdfpagemode = UseNone
}

\geometry{
  body={6.2in, 8.25in},
  left=1.2in,
  top=1.45in
}

\begin{document}

{\huge Leonid Petrov. Publication List}


\bigskip
\bigskip

\section*{Preprints ($*$), accepted, or published works}

\begin{etaremune}
\renewcommand{\labelenumi}{[\theenumi]}


\item ($*$)
Matthew Nicoletti, Leonid Petrov.
\emph{Irreversible Markov Dynamics and Hydrodynamics for KPZ States in the Stochastic Six Vertex Model}, 
\href{https://arxiv.org/abs/2201.?????}{\texttt{arXiv:2201.????? [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/39-6v.pdf}{\texttt{(PDF link)}}









\item ($*$)
Amol Aggarwal, Alexei Borodin, Leonid Petrov, Michael Wheeler.
\emph{Free Fermion Six Vertex Model: Symmetric Functions and Random Domino Tilings}, 
\href{https://arxiv.org/abs/2109.06718}{\texttt{arXiv:2109.06718 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/38-sl11.pdf}{\texttt{(PDF link)}}

















\item 
Leonid Petrov.
\emph{Refined Cauchy identity for spin Hall-Littlewood symmetric rational functions}, Journal of Combinatorial Theory Ser. A, vol. 184 (2021), 105519. 
\href{https://arxiv.org/abs/2007.10886}{\texttt{arXiv:2007.10886 [math.CO]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/37-publ-petrov-uva.pdf}{\texttt{(PDF link)}}







\item 
Matteo Mucciconi, Leonid Petrov.
\emph{Spin q-Whittaker polynomials and deformed quantum Toda}, Communications in Mathematical Physics, to appear. 
\href{https://arxiv.org/abs/2003.14260}{\texttt{arXiv:2003.14260 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/36-publ-petrov-uva.pdf}{\texttt{(PDF link)}}









\item 
Leonid Petrov, Mikhail Tikhonov.
\emph{Parameter symmetry in perturbed GUE corners process and reflected drifted Brownian motions}, Journal of Statistical Physics, 181 (2020), 1996–2010.. 
\href{https://arxiv.org/abs/1912.08671}{\texttt{arXiv:1912.08671 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/pert_GUE_symm.pdf}{\texttt{(PDF link)}}



\item 
Leonid Petrov.
\emph{Parameter permutation symmetry in particle systems and random polymers}, SIGMA 17 (2021), 021, 34 pages. 
\href{https://arxiv.org/abs/1912.06067}{\texttt{arXiv:1912.06067 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/symm_IPS.pdf}{\texttt{(PDF link)}}



\item 
Leonid Petrov.
\emph{PushTASEP in inhomogeneous space}, Electronic Journal of Probability, vol. 25 (2020), paper no. 114.. 
\href{https://arxiv.org/abs/1910.08994}{\texttt{arXiv:1910.08994 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/33-publ-petrov-uva.pdf}{\texttt{(PDF link)}}









\item 
Leonid Petrov, Axel Saenz.
\emph{Mapping TASEP back in time}, Probability Theory and Related Fields, online first (2021).. 
\href{https://arxiv.org/abs/1907.09155}{\texttt{arXiv:1907.09155 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/backwards_TASEP_preprint.pdf}{\texttt{(PDF link)}}







\item 
Alexey Bufetov, Matteo Mucciconi, Leonid Petrov.
\emph{Yang-Baxter random fields and stochastic vertex models}, Advances in Mathematics 388 (2021), 107865. 
\href{https://arxiv.org/abs/1905.06815}{\texttt{arXiv:1905.06815 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/31-publ-petrov-uva.pdf}{\texttt{(PDF link)}}















\item 
Ivan Corwin, Konstantin Matveev, Leonid Petrov.
\emph{The q-Hahn PushTASEP}, Intern. Math. Research Notices (2019),  rnz106. 
\href{https://arxiv.org/abs/1811.06475}{\texttt{arXiv:1811.06475 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/30-publ-petrov-uva.pdf}{\texttt{(PDF link)}}





\item 
Alisa Knizel, Leonid Petrov, Axel Saenz.
\emph{Generalizations of TASEP in discrete and continuous inhomogeneous space}, Communications in Mathematical Physics 372 (2019), no. 3, pp 797–864.. 
\href{https://arxiv.org/abs/1808.09855}{\texttt{arXiv:1808.09855 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/29-publ-petrov-uva.pdf}{\texttt{(PDF link)}}











\item 
Christian Gromoll, Mark Meckes, Leonid Petrov.
\emph{Quenched Central Limit Theorem in a Corner Growth Setting}, Electronic Communications in Probability (2018), Vol. 23, paper no. 101, 1-12. 
\href{https://arxiv.org/abs/1804.04222}{\texttt{arXiv:1804.04222 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/28-publ-petrov-uva.pdf}{\texttt{(PDF link)}}













\item 
Alexey Bufetov, Leonid Petrov.
\emph{Yang-Baxter field for spin Hall-Littlewood symmetric functions}, Forum of Mathematics Sigma 7 (2019), e39.. 
\href{https://arxiv.org/abs/1712.04584}{\texttt{arXiv:1712.04584 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/27-publ-petrov-uva.pdf}{\texttt{(PDF link)}}













\item 
Michael Damron, Leonid Petrov, David Sivakoff.
\emph{Coarsening model on  with biased zero-energy flips and an exponential large deviation bound for ASEP}, Communications in Mathematical Physics 362 (2018), no. 1, 185–217. 
\href{https://arxiv.org/abs/1708.05806}{\texttt{arXiv:1708.05806 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/26-publ-petrov-uva.pdf}{\texttt{(PDF link)}}

















\item 
Sevak Mkrtchyan, Leonid Petrov.
\emph{GUE corners limit of q-distributed lozenge tilings}, Electronic Journal of Probability, Volume 22 (2017), paper no. 101, 24 pp.. 
\href{https://arxiv.org/abs/1703.07503}{\texttt{arXiv:1703.07503 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/25-publ-petrov-uva.pdf}{\texttt{(PDF link)}}



\item 
Alexei Borodin, Leonid Petrov.
\emph{Inhomogeneous exponential jump model}, Probability Theory and Related Fields 172 (2018), 323-385. 
\href{https://arxiv.org/abs/1703.03857}{\texttt{arXiv:1703.03857 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/24-publ-petrov-uva-j.pdf}{\texttt{(PDF link)}}

















\item 
Daniel Orr, Leonid Petrov.
\emph{Stochastic higher spin six vertex model and q-TASEPs}, Advances in Mathematics 317 (2017), 473-525. 
\href{https://arxiv.org/abs/1610.10080}{\texttt{arXiv:1610.10080 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/23-publ-petrov-uva.pdf}{\texttt{(PDF link)}}









\item 
Vadim Gorin, Leonid Petrov.
\emph{Universality of local statistics for noncolliding random walks}, Ann. Probab. (2019), Vol. 47, No. 5, 2686-2753.. 
\href{https://arxiv.org/abs/1608.03243}{\texttt{arXiv:1608.03243 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/22-publ-petrov-uva-j.pdf}{\texttt{(PDF link)}}



\item 
Alexei Borodin, Leonid Petrov.
\emph{Lectures on Integrable probability: Stochastic vertex models and symmetric functions}, Lecture Notes of the Les Houches Summer School, Volume 104, July 2015. 
\href{https://arxiv.org/abs/1605.01349}{\texttt{arXiv:1605.01349 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/21-publ-petrov-uva.pdf}{\texttt{(PDF link)}}



\item 
Alexei Borodin, Leonid Petrov.
\emph{Higher spin six vertex model and symmetric rational functions}, Selecta Math. 24 (2018), no. 2, 751-874. 
\href{https://arxiv.org/abs/1601.05770}{\texttt{arXiv:1601.05770 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/20-publ-petrov-uva.pdf}{\texttt{(PDF link)}}









\item 
Konstantin Matveev, Leonid Petrov.
\emph{q-randomized Robinson-Schensted-Knuth correspondences and random polymers}, Annales de l’Institut Henri Poincare D: Combinatorics, Physics and their Interactions 4 (2017), no. 1, 1-123. 
\href{https://arxiv.org/abs/1504.00666}{\texttt{arXiv:1504.00666 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/19-publ-petrov-uva.pdf}{\texttt{(PDF link)}}





\item 
Ivan Corwin, Leonid Petrov.
\emph{Stochastic higher spin vertex models on the line}, Comm. Math. Phys. 343 (2016), no. 2, 651-700. 
\href{https://arxiv.org/abs/1502.07374}{\texttt{arXiv:1502.07374 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/18-publ-petrov-uva.pdf}{\texttt{(PDF link)}}













\item 
Alexei Borodin, Ivan Corwin, Leonid Petrov, Tomohiro Sasamoto.
\emph{Spectral theory for interacting particle systems solvable by coordinate Bethe ansatz}, Comm. Math. Phys. 339 (2015), no. 3, 1167–1245. 
\href{https://arxiv.org/abs/1407.8534}{\texttt{arXiv:1407.8534 [math-ph]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/17-publ-petrov-uva.pdf}{\texttt{(PDF link)}}





\item 
Alexey Bufetov, Leonid Petrov.
\emph{Law of Large Numbers for Infinite Random Matrices over a Finite Field}, Selecta Math. 21 (2015), no. 4, 1271–1338. 
\href{https://arxiv.org/abs/1402.1772}{\texttt{arXiv:1402.1772 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/16-publ-petrov.pdf}{\texttt{(PDF link)}}













\item 
Alexei Borodin, Leonid Petrov.
\emph{Integrable probability: From representation theory to Macdonald processes}, Probability Surveys, 11 (2014), 1-58. 
\href{https://arxiv.org/abs/1310.8007}{\texttt{arXiv:1310.8007 [math-ph]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/15-publ-petrov.pdf}{\texttt{(PDF link)}}





\item 
Alexei Borodin, Ivan Corwin, Leonid Petrov, Tomohiro Sasamoto.
\emph{Spectral theory for the q-Boson particle system}, Compositio Mathematica, 151 (2015), no. 1, 1-67. 
\href{https://arxiv.org/abs/1308.3475}{\texttt{arXiv:1308.3475 [math-ph]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/14-publ-petrov.pdf}{\texttt{(PDF link)}}



\item 
Ivan Corwin, Leonid Petrov.
\emph{The q-PushASEP: A New Integrable Model for Traffic in 1+1 Dimension}, Journal of Statistical Physics, 160 (2015), no. 4, 1005–1026. 
\href{https://arxiv.org/abs/1308.3124}{\texttt{arXiv:1308.3124 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/13-publ-petrov.pdf}{\texttt{(PDF link)}}





\item 
Alexei Borodin, Leonid Petrov.
\emph{Nearest neighbor Markov dynamics on Macdonald processes}, Advances in Mathematics, 300 (2016), 71-155. 
\href{https://arxiv.org/abs/1305.5501}{\texttt{arXiv:1305.5501 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/12-publ-petrov.pdf}{\texttt{(PDF link)}}









\item 
Leonid Petrov.
\emph{The Boundary of the Gelfand-Tsetlin Graph: New Proof of Borodin-Olshanski’s Formula, and its q-analogue}, Moscow Mathematical Journal, 14 (2014) no. 1, 121-160. 
\href{https://arxiv.org/abs/1208.3443}{\texttt{arXiv:1208.3443 [math.CO]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/11-publ-petrov.pdf}{\texttt{(PDF link)}}



\item 
Leonid Petrov.
\emph{Asymptotics of uniformly random lozenge tilings of polygons. Gaussian free field}, Annals of Probability, 43 (2014), no. 1, 1–43. 
\href{https://arxiv.org/abs/1206.5123}{\texttt{arXiv:1206.5123 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/10-publ-petrov.pdf}{\texttt{(PDF link)}}





\item 
Leonid Petrov.
\emph{Asymptotics of Random Lozenge Tilings via Gelfand-Tsetlin Schemes}, Probability Theory and Related Fields, 160 (2014), no. 3, 429–487. 
\href{https://arxiv.org/abs/1202.3901}{\texttt{arXiv:1202.3901 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/09-publ-petrov.pdf}{\texttt{(PDF link)}}







\item 
Leonid Petrov.
\emph{sl(2) Operators and Markov Processes on Branching Graphs}, Journal of Algebraic Combinatorics 38 (2013), no. 3, 663-720. 
\href{https://arxiv.org/abs/1111.3399}{\texttt{arXiv:1111.3399 [math.CO]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/08-publ-petrov.pdf}{\texttt{(PDF link)}}







\item 
Leonid Petrov.
\emph{On Measures on Partitions Arising in Harmonic Analysis for Linear and Projective Characters of the Infinite Symmetric Group}, Proceedings of the international conference "50 years of IITP". 
\href{https://arxiv.org/abs/1107.0676}{\texttt{arXiv:1107.0676 [math.CO]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/07-publ-petrov.pdf}{\texttt{(PDF link)}}





\item 
Leonid Petrov.
\emph{Pfaffian Stochastic Dynamics of Strict Partitions}, Electronic Journal of Probability 16 (2011), 2246-2295. 
\href{https://arxiv.org/abs/1011.3329}{\texttt{arXiv:1011.3329 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/06-publ-petrov.pdf}{\texttt{(PDF link)}}



\item 
Leonid Petrov.
\emph{Random Strict Partitions and Determinantal Point Processes}, Electronic Communications in Probability 15 (2010), 162-175. 
\href{https://arxiv.org/abs/1002.2714}{\texttt{arXiv:1002.2714 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/05-publ-petrov.pdf}{\texttt{(PDF link)}}







\item 
Leonid Petrov.
\emph{Random Walks on Strict Partitions}, Journal of Mathematical Sciences 168 (2010), no. 3, 437-463. 
\href{https://arxiv.org/abs/0904.1823}{\texttt{arXiv:0904.1823 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/04-publ-petrov.pdf}{\texttt{(PDF link)}}



\item 
Leonid Petrov.
\emph{Limit Behavior of Certain Random Walks on Strict Partitions}, Russian Mathematical Surveys 64 (2009), no. 6, 1139-1141. 
 \href{https://storage.lpetrov.cc/research_files/Petrov-publ/03-publ-petrov.pdf}{\texttt{(PDF link)}}



\item 
Leonid Petrov.
\emph{A Two-parameter Family of Infinite-dimensional Diffusions in the Kingman Simplex}, Functional Analysis and Its Applications 43 (2009), no. 4, 279-296. 
\href{https://arxiv.org/abs/0708.1930}{\texttt{arXiv:0708.1930 [math.PR]}}. \href{https://storage.lpetrov.cc/research_files/Petrov-publ/02-publ-petrov.pdf}{\texttt{(PDF link)}}



\item 
Leonid Petrov.
\emph{Asymptotic Behavior of a Certain Collection of Particles on a Line Under Synchronization}, Proceedings of the XXVIII Conference of Young Scientists of Department of Mechanics and Mathematics of the Lomonosov Moscow State University (2006), 152-156, in Russian. 
 \href{https://storage.lpetrov.cc/research_files/Petrov-publ/Asymptotic_Behavior.pdf}{\texttt{(PDF link)}}


\end{etaremune}

\subsection*{Other works}

\begin{etaremune}
	\renewcommand{\labelenumi}{[\theenumi]}
	\item
	Sihan Li, Andrew Mecca, Jeewoo Kim, Giusy Caprara, Elizabeth Wagner, Ting-Ting Du, Leonid Petrov, Wenhao Xu, Runjia Cui, Ivan Rebustini, Bechara Kachar, Anthony Peng, and Jung-Bum Shin,
	\emph{Myosin-VIIa is expressed in multiple isoforms and essential for tensioning the hair cell mechanotransduction complex}.
	Nature Communications, 11, Article number: 2066 (2020). \url{https://www.nature.com/articles/s41467-020-15936-z}.
\end{etaremune}


\end{document}
